Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-05-06 Manuscript/manuscript.Rmd
manuscript edits

## DISTANCE PROFILES HIGHLIGHT THE RELATIONSHIP BETWEEN KEY TFBS AND TAD BOUNDARIES

<!--
When evaluating the 10 kb data resolution, on GM12878, the distance profiles (on a $log_{2}$ scale) were found to be smaller for top predictive TFBS annotations in relation to genomic bins that overlapped with flanked TAD boundaries, when compared to bins that did not overlap with a flanked TAD boundary (Figure 7). At the same resolution and cell line, direct comparisons of quantiles obtained from the distribution of distances for the transcription factors SMC3a, ZNF143, CTCF, and RAD21, led to the the conclusion that these TFBS were more often located near TAD boundaries on the linear genome, as can be seen from the shifted quantile differences (Figure 7). Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12-17 A-D).
-->

>>>>

<!--
## DISTANCE PROFILES HIGHLIGHT THE RELATIONSHIP BETWEEN KEY TFBS AND TAD BOUNDARIES

When evaluating the 10 kb data resolution, on GM12878, the distance profiles (on a $log_{2}$ scale) were found to be smaller for top predictive TFBS annotations in relation to genomic bins that overlapped with flanked TAD boundaries, when compared to bins that did not overlap with a flanked TAD boundary (Figure 7). At the same resolution and cell line, direct comparisons of quantiles obtained from the distribution of distances for the transcription factors SMC3a, ZNF143, CTCF, and RAD21, led to the the conclusion that these TFBS were more often located near TAD boundaries on the linear genome, as can be seen from the shifted quantile differences (Figure 7). Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12-17 A-D).
-->
